An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}

### 2018-02-10 paper/ms.tex
bibtex now works

\author{\lightkurve contributors}
\affil{The galatic startup}

\author{August Muench}
\affiliation{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}
\collaboration{(AAS Journals Data Scientists collaboration)}

@@

\subsection{The \LightCurve~and \KeplerLightCurve~class}
        The \LightCurve~class is a simple cointainer to store \numpy~arrays
        (hereafter, arrays) related to flux time-domain measurements.

@@

        \begin{table}[!htb]
            \centering
            \caption{A subset of methods provided by the \LightCurve~class}
            \begin{tabular}{cp{5cm}}
                \hline
                \textbf{Method signature} & \textbf{Short description} \\
                \hline
                \texttt{stitch} & appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.\\
                \texttt{flatten} & applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.\\
                \texttt{fold} & folds a lightcurve at a given period and phase.\\
                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
                \texttt{cdpp} &  computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal. \\
                \texttt{plot} & displays a lightcurve.
            \end{tabular}
            \label{tab:methods}
        \end{table}

        A \LightCurve
        object can be instantiated by passing a \texttt{time} array, a
        \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
        which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
        \begin{verbatim}
        >>> from lightkurve import LightCurve
        >>> lc = LightCurve(time, flux)
        \end{verbatim}

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
\begin{verbatim}
>>> lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/"
... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=0.837495)
>>> klc.plot()
\end{verbatim}

@@

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{fig:plot-method}.
\begin{verbatim}
>>> import numpy as np
>>> from lightkurve import KeplerTargetPixelFile
>>> tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
>>> tpf.plot()
>>> tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

@@

An example of SAP flux correction for target \texttt{KOI 8462852}
(Tabby's star) can be written as follows
\begin{verbatim}
>>> from lightkurve.lightcurve import KeplerCBVCorrector
>>> cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
          ...                "0084/008462852/kplr008462852-2011073133259_llc.fits")
>>> cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

@@

Spacecraft-induced correlated noise remains one of the greatest hurdles to
analyzing K2 lightcurves. Many algorithms have been developed to mitigate
motion-dependent artifacts~\cite{vanderburg14}.

@@

We thank all the people that have made this AASTeX what it is today.  This
includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
for the new "modern" style design. Considerable help was provided via bug
reports and hacks from numerous people including Patricio Cubillos, Alex
Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
Gagne.

\vspace{5mm}
\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
CTIO:1.5m,CXO}

@@

\bibliographystyle{aasjournals}
\bibliography{ms}

>>>>

\author{\lightkurve~contributors}
\affil{The galatic startup}

\author{José Vinícius de Miranda Cardoso}
\affiliation{Bay Area Environmental Research Institute \\
Petaluma \\
California, USA}
\collaboration{(AAS Journals Data Scientists collaboration)}

@@

\subsection{The \LightCurve~and \KeplerLightCurve~classes}
        The \LightCurve~class is a simple cointainer to store \numpy~arrays
        (hereafter, arrays) related to flux time-domain measurements.

@@

        \begin{table}[!htb]
            \centering
            \caption{A subset of methods provided by the \LightCurve~class}
            \begin{tabular}{cp{6.5cm}}
                \hline
                \textbf{Method} & \textbf{Short description} \\
                \hline
                \texttt{stitch} & appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.\\
                \texttt{flatten} & applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.\\
                \texttt{fold} & folds a lightcurve at a given period and phase.\\
                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
                \texttt{cdpp} &  computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal. \\
                \texttt{plot} & displays a lightcurve.
            \end{tabular}
            \label{tab:methods}
        \end{table}

        A \LightCurve~object can be instantiated by passing a \texttt{time}
        array, a \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
        which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
\begin{verbatim}
>>> from lightkurve import LightCurve
>>> lc = LightCurve(time, flux)
\end{verbatim}

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
\begin{verbatim}
>>> lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.PDCSAP_FLUX.fold(period=0.837495)
>>> klc.plot()
\end{verbatim}

@@

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{fig:plot-method}.
\begin{verbatim}
>>> import numpy as np
>>> from lightkurve import KeplerTargetPixelFile
>>> tpf = KeplerTargetPixelFile("kplr008462852-2011073133259_lpd-targ.fits")
>>> tpf.plot()
>>> tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

@@

An example of SAP flux correction for target \texttt{KOI 8462852}
(Tabby's star) can be written as follows
\begin{verbatim}
>>> from lightkurve.lightcurve import KeplerCBVCorrector
>>> cbv = KeplerCBVCorrector("kplr008462852-2011073133259_llc.fits")
>>> cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

@@

Spacecraft-induced correlated noise remains one of the greatest hurdles to
analyzing K2 lightcurves. Many algorithms have been developed to mitigate
motion-dependent artifacts~\cite{vanderburg14}. In \lightkurve~we implement
an algorithm based off of~\cite{vanderburg14}

@@

We would like to express our gratitude...

\vspace{5mm}
\facilities{Kepler}

@@

\bibliographystyle{aasjournal}
\bibliography{ms}
